Parsing Postfix log files

### 2008-04-29 doc/logparser-other-parsers-review.tex
Tested lire. Logrep can't be tested, it doesn't work properly.

Like AWStats and Logrep, Lire attempts to correlate log lines by queueid,
but not by \pid{}, so the complete list of recipients for a mail should be
available; however its parser extracts only part of the available data and
makes no attempt to deal with the other complications described in
\sectionref{complications} \sectionref{additional complications}.
\parsername{} uses an \SQL{} database to make accessing the extracted data
as easy as possible.

\url{http://logreport.org/lire.html} \newline (Last checked 2007/10/09.)

>>>>

Like AWStats and Logrep, Lire attempts to correlate log lines by queueid,
but not by \pid{}, so the complete list of recipients for a mail should be
available; however its parser extracts only part of the available data and
makes no attempt to deal with the other complications described in
\sectionref{complications} \sectionref{additional complications}.
\parsername{} uses an \SQL{} database to make accessing the extracted data
as easy as possible.  When testing Lire on the \numberOFlogFILES{} test log
files it performed reasonably well, producing summaries of:

    \item Delivery status and failed deliveries.

    \item Sender and recipient domains and servers.

    \item Number of deliveries and bytes per day and hour.

    \item Recipients by domain.

    \item Deliveries by relays, by size and by delay.

    \item Delays by server and domain.

    \item Most mails exchanged between a pair of correspondents.

The numbers it reports appear reasonable, and the subset verified by the
author were correct.  Lire produces a report with less detail than
Pflogsumm, and is considerable harder to configure.

\url{http://logreport.org/lire.html} \newline (Last checked 2008/04/29.)
